---
title: "Plots markdown"
author: "Paige Lee"
date: "7/9/2020"
output: html_document
---

### Density plot of CG coverage of the first two samples of errbs5916

```{r, cache=FALSE}
library(tidyverse)
load("errbs5916_site_coverage_mat")
load("errbs5916_first_two_samples_10x_noNA.rda")
ggplot(two_columns_4, aes(x=Cpg.Coverage, color = Sample)) + geom_density() + xlim(c(0,1000))
```

### Boxplots of CG coverage of the first ten samples of errbs5916

```{r, cache=FALSE}
load("errbs5916_first_ten_samples_10x_noNA.rda")
ggplot(two_columns, aes(x=Sample, y=Cpg.Coverage)) + geom_boxplot(outlier.size = -1) + coord_flip(ylim = c(0,500))
```

### Boxplots of each project, comparing their numbers of CG units with at least 10x coverage

```{r, cache=FALSE}
load("all_projects.sample_count_mean.rda")
ggplot(p, aes(x=Project, y=Count)) + geom_boxplot() + coord_flip()
```

### Boxplots of each project, comparing their mean CG coverage (≥10x coverage)

```{r, cache=FALSE}
load("all_projects.sample_count_mean.rda")
ggplot(p, aes(x=Project, y=Mean)) + geom_boxplot() + coord_flip()
```

### Scatterplot of the number of CG units with at least 10x coverage in each project with the medians for each shown

```{r, cache=FALSE}
ggplot(p, aes(x=Project, y=Count)) + geom_point(size=2, aes(color = Project)) + coord_flip()
```

### Dot plot of the number of CG units with at least 10x coverage in each project with the medians for each shown

```{r, cache=FALSE}
ggplot(p, aes(x=Project, y=Count)) + geom_dotplot(binaxis="y", stackdir = "center", dotsize=0.3, aes(fill = Project)) + 
  coord_flip() + stat_summary(fun = median, fun.min = median, fun.max = median, geom = "crossbar", width = 0.5)
```

### Dot plot of the mean number of CG units with at least 10x coverage in each project with the medians for each shown

```{r, cache = FALSE}
ggplot(p, aes(x=Project, y=Mean)) + geom_dotplot(binaxis="y", stackdir = "center", dotsize=0.3, aes(fill = Project)) + 
  coord_flip() + stat_summary(fun = median, fun.min = median, fun.max = median, geom = "crossbar", width = 0.5)
```

### Boxplots of each project, comparing their numbers of CG units with at least 5x coverage

```{r, cache=FALSE}
load("all_projects.sample_count_mean_5x.rda")
ggplot(q, aes(x=Project, y=Count)) + geom_boxplot() + coord_flip()
```

### Boxplots of each project, comparing their mean CG coverage with at least 5x coverage

```{r, cache=FALSE}
ggplot(q, aes(x=Project, y=Mean)) + geom_boxplot() + coord_flip()
```

### Scatterplot of the number of CG units with at least 5x coverage in each project with the medians for each shown

```{r, cache=FALSE}
ggplot(q, aes(x=Project, y=Count)) + geom_point(size=2, aes(color = Project)) + coord_flip() + 
  stat_summary(fun = median, fun.min = median, fun.max = median, geom = "crossbar", width = 0.5)
```

### Dot plot of the number of CG units with at least 5x coverage in each project with the medians for each shown

```{r, cache = FALSE}
ggplot(q, aes(x=Project, y=Count)) + geom_dotplot(binaxis="y", stackdir = "center", dotsize=0.3, aes(fill = Project)) + 
  coord_flip() + stat_summary(fun = median, fun.min = median, fun.max = median, geom = "crossbar", width = 0.5)
```
